Add a sound file and play back at a given time, with asynchronous file access.
%
This plugin provides an alternative to the sndfile audio plugin
(see \ref{sec:ap_sndfile}). It does not require to load the full
file during session load, which can be advantageous for huge files. As
a drawback, it is not possible to configure absolute RMS value, and
dropouts may occur if the file system is slower than required.
%
If the plugin receives multiple channels (e.g., when used in a
receiver or a diffuse sound field), all channels starting at channel
number \attr{channel} will be returned. If the file does not contain a
sufficient number of channels, silcence will be returned for all
channels not available in the sound file.

\begin{tscattributes}
  \indattr{name}        & Sound file name.                                            \\
  \indattr{channel}     & First sound file channel to be used, zero-base (default: 0) \\
  \indattr{position}    & Start position within the scene, in seconds (default: 0).   \\
  \indattr{loop}        & loop count or 0 for infinite looping (default: 1).          \\
  \indattr{caliblevel}  & Calibration level in dB SPL (default: 93.979).              \\
  \indattr{transport}   & Use session time base (default: true)                       \\
  \indattr{license}     & License form of session file                                \\
  \indattr{attribution} & Attribution of session file, e.g., author name              \\
  \indattr{mute}        & Mute flag                                                   \\
\end{tscattributes}
%

93.979~dB corresponds internally to a full-scale signal.
