The \texttt{oscrelay} module acts as a bridge for Open Sound Control
(OSC) messages. It listens for incoming OSC messages, including
directly dispatched messages, matching a specific path and forwards
them to a defined target URL. This module supports path filtering,
path modification, and message content replacement.

The module is configured using the following attributes within the XML configuration:

\input{modtabtex/taboscrelay.tex}

\subsubsection*{Message Replacement}

When the \texttt{replacemsg} attribute is enabled, the module forwards a custom message instead of the original data. This custom message is constructed using child elements within the module's XML definition. The following child elements are supported:

\begin{itemize}
    \item \elem{f v="..."}: Adds a float value to the message.
    \item \elem{i v="..."}: Adds an integer (int32) value to the message.
    \item \elem{s v="..."}: Adds a string value to the message.
\end{itemize}

\subsubsection*{Examples}

{\bf Basic Relay:} Forward all incoming messages to a remote server on
port 9000:
\begin{lstlisting}[numbers=none]
<oscrelay path="/" url="osc.udp://192.168.1.50:9000/" />
\end{lstlisting}

{\bf Path Filtering and Trimming:} Listen for messages starting
with \texttt{/sensor/}, remove that prefix, and forward the rest to
localhost:
\begin{lstlisting}[numbers=none]
<oscrelay path="/" 
          url="osc.udp://localhost:9000/" 
          startswith="/sensor/" 
          trimstart="true" />
\end{lstlisting}
{Example:} An incoming message \texttt{/sensor/temp} is forwarded as \texttt{/temp}.


{\bf Message Replacement:} Replace any incoming message
on \texttt{/trigger} with a specific integer command:
\begin{lstlisting}[numbers=none]
<oscrelay path="/trigger" 
          url="osc.udp://localhost:9000/" 
          replacemsg="true">
    <i v="1" />
</oscrelay>
\end{lstlisting}
