Horizontal higher-order Ambisonics with embedded decoder, for regular
loudspeaker layouts.

\begin{lstlisting}[numbers=none]
<receiver type="hoa2d" order="3" maxre="true">...</receiver>
\end{lstlisting}

This receiver type provides horizontal higher order ambisonics with
basic or $\max r_E$ decoding.
%
If \attr{order} is zero or unset, then the maximum possible order for
the given number of loudspeakers is used.

\input{tabreceiverhoa2d.tex}

\begin{tscattributes}
\indattr{order}            & Ambisonics order; 0: use maximum possible (default: 0)                                                                      \\
\indattr{rotation}         & Rotation of the loudspeaker array in degrees (default: compensate average speaker rotation)                                 \\
\indattr{maxre}            & Use $\max r_E$ decoder (true) or basic decoder (false) (default: false)                                                     \\
\indattr{diffup}           & Use diffuse upsampling similar to \citet{Zotter2014} (default: false)                                                       \\
\indattr{diffup\_rot}      & Decorrelation rotation in degrees (default: 45)                                                                              \\
\indattr{diffup\_delay}    & Decorrelation delay in seconds (default: 0.01)                                                                              \\
\indattr{diffup\_maxorder} & Maximum order of diffuse sound fields (default: 100)                                                                        \\
\indattr{filtershape}      & De-correlation filter shape for source width encoding, one of ``none'' (default), ``notch'', ``sine'', ``tria'', ``triald'' \\
\indattr{filterperiod}     & Filter period in seconds for source width encoding (default: 0.005)                                                         \\
\end{tscattributes}

\paragraph{Note:}
Only regular speaker arrays can be used. Explicit speaker
distributions are ignored, and a regular speaker distribution with
counter-clockwise azimuths is assumed, with the first speaker starting
at the value provided in the \attr{rotation} attribute.
%
If the \attr{rotation} attribute is not given, then the average
difference between a regular layout and the explicit speaker azimuth
is taken as \attr{rotation}.

If \indattr{diffup} is set to ``true'', diffuse-decoding is using the
internal decoder, which is also used for decoding of panned sources.
%
If \indattr{diffup} is set to ``false'', the standard speaker-based
diffuse render method is applied.
%
Source-width encoding splits the signal into two uncorrelated signals
and creates virtual sound sources separated by the source width.

An alternative receiver type \verb!hoa2d_fuma! can be used to return
the encoded signal in FuMa normalization and ACN channel sequence.
